---
title: "ML Project"
output: html_document
---

# Introduction

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. 

```{r, eval=FALSE}
library(dplyr); 
library(caret); 
```

```{r, eval=FALSE}

file.url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(file.url, destfile = "pml-training.csv", method = "curl")
```
```{r}
training <- read.csv("pml-training.csv", na.string = c("", "NA"))
dim(training)

```

From this we can see that there are 19622 observations of 160 variables. Drop the variables that won't help with prediction.  It makes sense to remove all rows where new_window = Yes, since those are summary rows. We will also remove all columns that only have NA values.


```{r}
 training <- subset(training, new_window == "no")

  ##remove NA values
  training <- Filter(function(x)!all(is.na(x)), training)
  dim(training)
```

We will remove  will remove the date/time, window, and user columns.

```{r}
 colsToRemove <-  c( "user_name", "raw_timestamp_part_1","raw_timestamp_part_2", "cvtd_timestamp","new_window","num_window")
  
  training <- training[,!(names(training) %in% colsToRemove)] 
 dim(training)
```

Now our dataset of 54 variables and 19,216 observations.In order to perform some cross validation, we will split the training dataset into a training and test set.

```{r}
library(caret)
inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE) 
training <-training[inTrain,] 
testing <- training[-inTrain,]
```

#Model Selection
### Linear Discriminant Analysis

It is similar to logistic regression, it is more naturally suited to classification problems like this one where the outcome variable is multinomial.

```{r}
# Fit a linear discriminant model
fit.lda <- train(classe ~ .,
             method = "lda",
             data = training)
pred.lda <- predict(fit.lda, newdata = testing)
confusionMatrix(pred.lda, testing$classe)$overall[1]
```
