---
title: "ML Project"
output: html_document
---

# Introduction

The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. 

```{r}
library(dplyr)
library(caret)
library(doParallel)

```

```{r}

file.url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
download.file(file.url, destfile = "pml-training.csv", method = "wget")

training <- read.csv("pml-training.csv", na.string = c("", "NA"))
dim(training)

```

From this we can see that there are 19622 observations of 160 variables. Drop the variables that won't help with prediction.  It makes sense to remove all rows where new_window = Yes, since those are summary rows. We will also remove all columns that only have NA values.


```{r}
 training <- subset(training, new_window == "no")

  ##remove NA values
  training <- Filter(function(x)!all(is.na(x)), training)
  dim(training)
```

We will remove  will remove the date/time, window, and user columns.

```{r}
 colsToRemove <-  c( "user_name", "raw_timestamp_part_1","raw_timestamp_part_2", "cvtd_timestamp","new_window","num_window")
  
  training <- training[,!(names(training) %in% colsToRemove)] 
 dim(training)
```

Now our dataset of 54 variables and 19,216 observations.In order to perform some cross validation, we will split the training dataset into a training and test set.

```{r}

inTrain <- createDataPartition(y=training$classe, p=0.75, list=FALSE) 
training <-training[inTrain,] 
testing <- training[-inTrain,]
```

#Model Selection
### Random Forest
Create a cluster with `doParallel` to use 8 parallel threads.
```{r}
cl <- makeCluster(8)
registerDoParallel(8)
```


```{r}
fit <- train(classe~.,data=training, method="rf",trControl=trainControl(method = "cv"))
stopCluster(cl)
pred <- predict(fit, newdata = testing)
confusionMatrix(pred, testing$classe)$overall[1]
```

```{r}

pml_write_files = function(x){
    n = length(x)
    for(i in 1:20){
        filename = paste0("problem_id_",i,".txt")
        write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
}

pml_write_files(pred)
```
